Solar wind prediction for the Solar Probe Plus orbit

### 2017-05-28 paperMVVB/sections/acknowledgments.tex
consistent variable naming; streamlined some sentences

\begin{acknowledgements}
	This work was done within the scope of the Coronagraphic German~and~US SolarProbePlus Survey (CGAUSS), funded by the German Aerospace Center (DLR) (grant number...).\\
	The authors thank the Helios and OMNI PIs/teams for creating and making available the solar wind in situ data. The Helios and the OMNI data are supplied by the NASA Space Science Data Coordinated Archive (NSSDCA) and the Space Physics Data Facility (SPDF) at NASA's Goddard Space Flight Center (GSFC).\\
	Additional thanks for maintaining and providing the international sunspot number series goes to the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO) at the Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).\\
%	We thank the referees for /very important comments and suggestions. /careful review of this paper.

>>>>

\begin{acknowledgements}
	This work was done within the scope of the Coronagraphic German~and~US SolarProbePlus Survey (CGAUSS), funded by the German Aerospace Center (DLR) (grant number...).\\
	The authors thank the Helios and OMNI PIs/teams for creating and making available the solar wind in situ data. The Helios and the OMNI data are supplied by the NASA Space Science Data Coordinated Archive (NSSDCA) and the Space Physics Data Facility (SPDF) at NASA's Goddard Space Flight Center (GSFC).\\
	Additional thanks for maintaining and providing the international sunspot number series goes to the World Data Center -- Sunspot Index and Long-term Solar Observations (WDC-SILSO) at the Solar Influences Data Analysis Center (SIDC), Royal Observatory of Belgium (ROB).\\
	The SPP SPICE kernel was kindly provided by Angelos~Vourlidas.\\
%	We thank the referees for /very important comments and suggestions. /careful review of this paper.
